Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-30 doc/paper.Rmd
mini edits

```{r profile-sketch, fig.height = 3, fig.width='\\textwidth'}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

profile$l25 <- predict(loess(data = profile, value~y, span=.25))
profile$l50 <- predict(loess(data = profile, value~y, span=.5))
profile$l75 <- predict(loess(data = profile, value~y, span=.75))
profile$l100 <- predict(loess(data = profile, value~y, span=2))

pw1 <- profile %>%
  ggplot(aes(x = y, y = value-lw25)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.25")

pw2 <- profile %>%
  ggplot(aes(x = y, y = value-lw50)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.5")

pw3 <- profile %>%
  ggplot(aes(x = y, y = value-lw75)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.75")

pw4 <- profile %>%
  ggplot(aes(x = y, y = value-lw100)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 1")

p1 <- profile %>%
  ggplot(aes(x = y, y = value-l25)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.25")

p2 <- profile %>%
  ggplot(aes(x = y, y = value-l50)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.5")

p3 <- profile %>%
  ggplot(aes(x = y, y = value-l75)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 0.75")

p4 <- profile %>%
  ggplot(aes(x = y, y = value-l100)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Coarseness 1")

prof  <- profile %>% ggplot(aes (x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")
grid.arrange(pw1, pw2, pw3, pw4, p1, p2, p3, p4, prof, ncol=4)
```

>>>>

```{r profile-sketch, fig.height = 2.5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles}. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

profiles <- tidyr::gather(profile, coarseness, values, lw25:lw75)
profiles <- profiles %>% mutate(
  c = readr::parse_number(coarseness)/100
)
profiles %>% 
  ggplot(aes(x = y, y = value-values)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) +
  facet_grid(~c, labeller="label_both")
